---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 


```{r}
devtools::install_github("VerbalExpressions/RVerbalExpressions")
```

```{r}
library(RVerbalExpressions)
library(lubridate)
```


# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 




```{r}
floor_date(today(), unit = "year") + months(0:11)
```


Write a function that given your birthday (as a date), returns how old you are in years.

```{r}
my_birthday <- function(birthday) {
  as.numeric(as.duration(today() - birthday), "years") %/% 1
}
birthday <- ymd(19950806)
my_birthday(birthday)
```


Write a function that given your birthday, returns the day of the week you were born on. 


```{r}

my_birthday_weekday <- function(birthday) {
  wday(birthday)
}
birthday <- ymd(19950806)
my_birthday_weekday(birthday)


```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)




Regular expressions:
```{r}

str_view(stringr::words, ".......", match = TRUE)

```
Rverbalexpressions:
```{r}
allwords<-stringr::words

seven_letters_more <- rx() %>% 
  rx_start_of_line() %>% 
  rx_word_char() %>%
  rx_repeat_previous(7) %>%
  rx_anything() %>% 
  rx_end_of_line() %>% 
  print()

str_view(allwords,seven_letters_more, match = T)

```



## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

Regular expressions:

```{r}
a<-str_detect(stringr::words, "^[^aeiou]+$")
word_list[a]

```


Rverbalexpressions:

```{r}
no_vowel <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but('aeiou') %>% 
  rx_end_of_line()

word_list[str_detect(stringr::words, no_vowel)]
```


Empirically verify the rule “i before e except after c”.

Regular expressions
```{r}
word_list[str_detect(stringr::words, "([^c]ie)")]
```
Rverbalexpressions:
```{r}
rule_NOc_ie <- rx() %>% 
  rx_anything_but("c") %>% 
  rx_find("ie") %>% 
  print()

word_list[str_detect(stringr::words,rule_NOc_ie)]

```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

Regular expressions:
Phone numbers have a format like `123-456-7890` or "123.456.7890"
```{r}
x <- c("123.456.7890","123-456-7890", "(123)456-7890")
grepl("^\\d{3}[-.]\\d{3}[-.]\\d{4}$",x)
```
Phone numbers have a format like (123)456-7890
```{r}
grepl("^\\(\\d{3}\\)\\d{3}-\\d{4}$",x)
```


Rverbalexpressions:
Phone numbers have a format like `123-456-7890` or "123.456.7890"
```{r}
telrx_US_1<-rx() %>%
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() %>% 
  grepl(c("123.456.7890","123-456-7890", "(123)456-7890")) %>% 
  print()
```
Phone numbers have a format like (123)456-7890

```{r}
telrx_US_2<-rx() %>%
  rx_start_of_line() %>% 
  rx_find("(") %>%
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_find(")") %>%
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() %>% 
  grepl(c("123.456.7890","123-456-7890", "(123)456-7890")) %>% 
  print()

```


# Part 2
# In this part, please look my 10-import-qianyi.rmd and 30-feature-engineering-qianyi.rmd.

Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data.  

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

I want to use these sections to replace my score for my coding portion of assignment 3.

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended.  

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

